NHF1 Tandem Deamination Data Generation

### 2022-06-15 R/NHF1GeneralReadSequenceFigureGeneration.rmd
Update NHF1 notebooks
- Support for all_reps
- Read length counting occurs during data generation
- Temporarily removed chunks with adjusted y-axis from minimum read length filtering

expansionOffset = 10
cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)

@@

```{r read_sequence_frequencies}
CPDTGGSeqFreq = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints)
for (i in seq_along(CPDTGGSeqFreq)) {
  for (j in seq_along(CPDTGGSeqFreq[[i]])) {
    CPDTGGSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDTGGSeqFreq)[i],
      timepoint = names(CPDTGGSeqFreq[[i]])[j], sequence = "TGG"
    ))
  }
}

CPDCGASeqFreq = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints)
for (i in seq_along(CPDCGASeqFreq)) {
  for (j in seq_along(CPDCGASeqFreq[[i]])) {
    CPDCGASeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDCGASeqFreq)[i],
      timepoint = names(CPDCGASeqFreq[[i]])[j], sequence = "CGA"
    ))
  }
}

sixFourTGGSeqFreq = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints)
for (i in seq_along(sixFourTGGSeqFreq)) {
  for (j in seq_along(sixFourTGGSeqFreq[[i]])) {
    sixFourTGGSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(sixFourTGGSeqFreq)[i],
      timepoint = names(sixFourTGGSeqFreq[[i]])[j], sequence = "TGG"
    ))
  }
}

sixFourCGASeqFreq = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints)
for (i in seq_along(sixFourCGASeqFreq)) {
  for (j in seq_along(sixFourCGASeqFreq[[i]])) {
    sixFourCGASeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(sixFourCGASeqFreq)[i],
      timepoint = names(sixFourCGASeqFreq[[i]])[j], sequence = "CGA"
    ))
  }
}
```

```{r CPD_sequence_frequencies, fig.width = 11, fig.height = 10}
plotSequenceFrequencies(CPDTGGSeqFreq$rep1,
                        title = "CPD TGG Frequencies Rep1", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("TGG"))
plotSequenceFrequencies(CPDTGGSeqFreq$rep2,
                        title = "CPD TGG Frequencies Rep2", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("TGG"))

plotSequenceFrequencies(CPDCGASeqFreq$rep1,
                        title = "CPD CGA Frequencies Rep1", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("CGA"))
plotSequenceFrequencies(CPDCGASeqFreq$rep2,
                        title = "CPD CGA Frequencies Rep2", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("CGA"))
```

```{r 6-4_sequence_frequencies, fig.width = 11, fig.height = 10}
plotSequenceFrequencies(sixFourTGGSeqFreq$rep1,
                        title = "6-4 TGG Frequencies Rep1", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("TGG"))
plotSequenceFrequencies(sixFourTGGSeqFreq$rep2,
                        title = "6-4 TGG Frequencies Rep2", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("TGG"))

plotSequenceFrequencies(sixFourCGASeqFreq$rep1,
                        title = "6-4 CGA Frequencies Rep1", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("CGA"))
plotSequenceFrequencies(sixFourCGASeqFreq$rep2,
                        title = "6-4 CGA Frequencies Rep2", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("CGA"))
```

@@

  readData = timepoints
  for (i in seq_along(readData)) {
    readData[[i]] = fread(generateFilePath(
      generalReadSequenceDataDirectory, dataTypeStrings$alignedReads, ".bed",
      cellType = cellType, lesion = lesion, timepoint = names(readData)[i],
      repitition = repitition, expansionNum = expansionOffset
    ))
    readData[[i]] = data.table(Read_Length = nchar(readData[[i]]$V7)-expansionOffset*2,
                               Timepoint = names(readData)[i])
    readData[[i]] = readData[[i]][Read_Length >= 15 & Read_Length <= 31]
  }

  plotReadLengthFrequencies(readData,
                            title = paste(c(lesion, "Read Length Freq",
                                            tools::toTitleCase(repitition)),
                                          collapse = ' '))

@@

```{r CPD_read_length_frequencies}
readAndPlotReadLengthFrequencies("CPD", "rep1", CPDTimepoints)
readAndPlotReadLengthFrequencies("CPD", "rep2", CPDTimepoints)
```

```{r 6-4_read_length_frequencies}
readAndPlotReadLengthFrequencies("6-4", "rep1", sixFourTimepoints)
readAndPlotReadLengthFrequencies("6-4", "rep2", sixFourTimepoints)
```

>>>>

expansionOffset = 10
cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
repNames = c("rep1", "rep2", "all_reps")
minReadLength = 22; maxReadLength = 30

@@

```{r read_sequence_frequencies}
CPDTGGSeqFreq = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints, all_reps = CPDTimepoints)
for (i in seq_along(CPDTGGSeqFreq)) {
  for (j in seq_along(CPDTGGSeqFreq[[i]])) {
    CPDTGGSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDTGGSeqFreq)[i],
      timepoint = names(CPDTGGSeqFreq[[i]])[j], sequence = "TGG"
    ))
  }
}

CPDCGASeqFreq = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints, all_reps = CPDTimepoints)
for (i in seq_along(CPDCGASeqFreq)) {
  for (j in seq_along(CPDCGASeqFreq[[i]])) {
    CPDCGASeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDCGASeqFreq)[i],
      timepoint = names(CPDCGASeqFreq[[i]])[j], sequence = "CGA"
    ))
  }
}

sixFourTGGSeqFreq = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints, all_reps = sixFourTimepoints)
for (i in seq_along(sixFourTGGSeqFreq)) {
  for (j in seq_along(sixFourTGGSeqFreq[[i]])) {
    sixFourTGGSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(sixFourTGGSeqFreq)[i],
      timepoint = names(sixFourTGGSeqFreq[[i]])[j], sequence = "TGG"
    ))
  }
}

sixFourCGASeqFreq = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints, all_reps = sixFourTimepoints)
for (i in seq_along(sixFourCGASeqFreq)) {
  for (j in seq_along(sixFourCGASeqFreq[[i]])) {
    sixFourCGASeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(sixFourCGASeqFreq)[i],
      timepoint = names(sixFourCGASeqFreq[[i]])[j], sequence = "CGA"
    ))
  }
}
```

```{r CPD_sequence_frequencies, fig.width = 11, fig.height = 10}
for (i in seq_along(CPDTGGSeqFreq)) {
  plotSequenceFrequencies(CPDTGGSeqFreq[[i]],
                          title = "CPD TGG Frequencies", repNames[i], expansionOffset = expansionOffset,
                          showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                          querySequences = c("TGG"))
}

for (i in seq_along(CPDCGASeqFreq)) {
  plotSequenceFrequencies(CPDCGASeqFreq[[i]],
                          title = "CPD CGA Frequencies", repNames[i], expansionOffset = expansionOffset,
                          showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                          querySequences = c("CGA"))
}
```

```{r 6-4_sequence_frequencies, fig.width = 11, fig.height = 10}
for (i in seq_along(sixFourTGGSeqFreq)) {
  plotSequenceFrequencies(sixFourTGGSeqFreq[[i]],
                          title = "6-4 TGG Frequencies", repNames[i], expansionOffset = expansionOffset,
                          showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                          querySequences = c("TGG"))
}

for (i in seq_along(sixFourCGASeqFreq)) {
  plotSequenceFrequencies(sixFourCGASeqFreq[[i]],
                          title = "6-4 CGA Frequencies", repNames[i], expansionOffset = expansionOffset,
                          showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                          querySequences = c("CGA"))
}
```

@@

  readLengthCountsByTimepoint = timepoints
  for (i in seq_along(readLengthCountsByTimepoint)) {
    readLengthCountsByTimepoint[[i]] = fread(generateFilePath(
      generalReadSequenceDataDirectory, dataTypeStrings$readLengthcounts, ".tsv",
      cellType = cellType, lesion = lesion, timepoint = names(readLengthCountsByTimepoint)[i],
      repitition = repitition
    ))
  }

  plotReadLengthFrequencies(readLengthCountsByTimepoint,
                            title = paste(lesion, "Read Length Freq", repitition))

@@

```{r CPD_read_length_frequencies}
for (rep in repNames) {
  readAndPlotReadLengthFrequencies("CPD", rep, CPDTimepoints)
}
```

```{r 6-4_read_length_frequencies}
for (rep in repNames) {
readAndPlotReadLengthFrequencies("6-4", rep, sixFourTimepoints)
}
```

### 2022-06-15 R/NHF1TandemDeaminationDataGeneration.rmd
Update NHF1 notebooks
- Support for all_reps
- Read length counting occurs during data generation
- Temporarily removed chunks with adjusted y-axis from minimum read length filtering

```{r read_mismatch_data}
# Get file paths for the mismatch by read data
CPDMismatchData = list(rep1 = CPDTimepoints,
                       rep2 = CPDTimepoints)
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    CPDMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
      repitition = names(CPDMismatchData)[i], filtering = filtering,
      includedMismatches = mismatchType
      ))
  }
}

sixFourMismatchData = list(rep1 = sixFourTimepoints,
                           rep2 = sixFourTimepoints)
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
      repitition = names(sixFourMismatchData)[i], filtering = filtering,
      includedMismatches = mismatchType
      ))
  }
}
```

@@

```{r generate_and_write_mismatch_position_statistics_by_read_length_and_timepoint}
CPDGroupedStats = list(rep1 = list(), rep2 = list())
CPDGroupedStats$rep1$three_prime = getGroupedPositionStats(CPDMismatchData$rep1)
CPDGroupedStats$rep2$three_prime = getGroupedPositionStats(CPDMismatchData$rep2)
CPDGroupedStats$rep1$five_prime = getGroupedPositionStats(CPDMismatchData$rep1, posType = FIVE_PRIME)
CPDGroupedStats$rep2$five_prime = getGroupedPositionStats(CPDMismatchData$rep2, posType = FIVE_PRIME)

sixFourGroupedStats = list(rep1 = list(), rep2 = list())
sixFourGroupedStats$rep1$three_prime = getGroupedPositionStats(sixFourMismatchData$rep1)
sixFourGroupedStats$rep2$three_prime = getGroupedPositionStats(sixFourMismatchData$rep2)
sixFourGroupedStats$rep1$five_prime =
  getGroupedPositionStats(sixFourMismatchData$rep1, posType = FIVE_PRIME)
sixFourGroupedStats$rep2$five_prime =
  getGroupedPositionStats(sixFourMismatchData$rep2, posType = FIVE_PRIME)

@@

```{r read_expanded_mismatch_data}
# Get file paths for the expanded mismatch by read data
CPDMismatchData = list(rep1 = CPDTimepoints,
                       rep2 = CPDTimepoints)
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    CPDMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
      repitition = names(CPDMismatchData)[i], expansionNum = expansionOffset, filtering = filtering,
      includedMismatches = mismatchType
      ))
  }
}

sixFourMismatchData = list(rep1 = sixFourTimepoints,
                           rep2 = sixFourTimepoints)
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
      repitition = names(sixFourMismatchData)[i], expansionNum = expansionOffset, filtering = filtering,
      includedMismatches = mismatchType
      ))
  }
}
```

@@

# Read mismatch frequency z-scores.
CPDMMFreqZScores = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints)
for (i in seq_along(CPDMMFreqZScores)) {
  for (j in seq_along(CPDMMFreqZScores[[i]])) {
    CPDMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDMMFreqZScores)[i],
      timepoint = names(CPDMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

sixFourMMFreqZScores = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints)
for (i in seq_along(sixFourMMFreqZScores)) {
  for (j in seq_along(sixFourMMFreqZScores[[i]])) {
    sixFourMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(sixFourMMFreqZScores)[i],
      timepoint = names(sixFourMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

>>>>

```{r read_mismatch_data}
# Get file paths for the mismatch by read data
CPDMismatchData = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints, all_reps = CPDTimepoints)
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    CPDMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
      repitition = names(CPDMismatchData)[i], filtering = filtering,
      includedMismatches = mismatchType
      ))
  }
}

sixFourMismatchData = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints, all_reps = sixFourTimepoints)
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
      repitition = names(sixFourMismatchData)[i], filtering = filtering,
      includedMismatches = mismatchType
      ))
  }
}
```

@@

```{r generate_and_write_read_length_counts}
CPDReadLengthCounts = lapply(CPDMismatchData, function(x) lapply(
  x, function(y) {
    y[, .N, by = Read_Length][order(Read_Length)]
  }
))

sixFourReadLengthCounts = lapply(sixFourMismatchData, function(x) lapply(
  x, function(y) {
    y[, .N, by = Read_Length][order(Read_Length)]
  }
))

for (i in seq_along(CPDReadLengthCounts)) {
  for (j in seq_along(CPDReadLengthCounts[[i]])) {
    fwrite(CPDReadLengthCounts[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$readLengthcounts, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDReadLengthCounts)[i],
      timepoint = names(CPDReadLengthCounts[[i]])[j], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

for (i in seq_along(sixFourReadLengthCounts)) {
  for (j in seq_along(sixFourReadLengthCounts[[i]])) {
    fwrite(sixFourReadLengthCounts[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$readLengthcounts, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(sixFourReadLengthCounts)[i],
      timepoint = names(sixFourReadLengthCounts[[i]])[j], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}
```

```{r generate_and_write_mismatch_position_statistics_by_read_length_and_timepoint}
CPDGroupedStats = list(rep1 = list(), rep2 = list(), all_reps = list())
for (i in seq_along(CPDGroupedStats)) {
  CPDGroupedStats[[i]]$three_prime = getGroupedPositionStats(CPDMismatchData[[i]])
  CPDGroupedStats[[i]]$five_prime = getGroupedPositionStats(CPDMismatchData[[i]], posType = FIVE_PRIME)
}

sixFourGroupedStats = list(rep1 = list(), rep2 = list(), all_reps = list())
for (i in seq_along(sixFourGroupedStats)) {
  sixFourGroupedStats[[i]]$three_prime = getGroupedPositionStats(sixFourMismatchData[[i]])
  sixFourGroupedStats[[i]]$five_prime =
    getGroupedPositionStats(sixFourMismatchData[[i]], posType = FIVE_PRIME)
}

@@

```{r read_expanded_mismatch_data}
# Get file paths for the expanded mismatch by read data
CPDMismatchData = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints, all_reps = CPDTimepoints)
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    CPDMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
      repitition = names(CPDMismatchData)[i], expansionNum = expansionOffset, filtering = filtering,
      includedMismatches = mismatchType
      ))
  }
}

sixFourMismatchData = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints, all_reps = sixFourTimepoints)
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
      repitition = names(sixFourMismatchData)[i], expansionNum = expansionOffset, filtering = filtering,
      includedMismatches = mismatchType
      ))
  }
}
```

@@

# Read mismatch frequency z-scores.
CPDMMFreqZScores = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints, all_reps = CPDTimepoints)
for (i in seq_along(CPDMMFreqZScores)) {
  for (j in seq_along(CPDMMFreqZScores[[i]])) {
    CPDMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDMMFreqZScores)[i],
      timepoint = names(CPDMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

sixFourMMFreqZScores = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints, all_reps = sixFourTimepoints)
for (i in seq_along(sixFourMMFreqZScores)) {
  for (j in seq_along(sixFourMMFreqZScores[[i]])) {
    sixFourMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(sixFourMMFreqZScores)[i],
      timepoint = names(sixFourMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}
